Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-01-19 writeup/paper-names.tex
rewired figure paths

\begin{figure}
    \centering
    \includegraphics[scale=.4]{figures/pareto-plane-iso-best-balanced-legend.pdf}
    \caption{Predictability and parseability of 51 UD languages (red), indicated by ISO codes, compared to ten baseline word order grammars per language (green). Predictability and parseability scores are $z$-scored within language. Each point for a real language has a line pointing in the direction of the center of mass of its baselines. The green contour shows the density of baseline languages. Unlabeled dots represent the centroid for real languages (red), baseline languages (green), and languages optimized for predictability (yellow), parseability (pink), efficiency (blue), and dependency length (red). When a language is to the bottom--left of its baselines, this indicates that it is relatively optimal for efficiency.} % TODO colors, fontsize, etc could conceivably be made prettier
    \label{fig:pareto-plane}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.2]{figures/posterior-satisfied-universals-efficiency.pdf}
     \includegraphics[scale=.2]{figures/posterior-satisfied-universals-langmod.pdf}
     \includegraphics[scale=.2]{figures/posterior-satisfied-universals-parseability.pdf}
    \includegraphics[scale=.2]{figures/posterior-satisfied-universals-depl.pdf}
	\caption{Posterior of the number of correlations predicted in the direction found in the UD treebanks.}
    \label{fig:posterior-satisfied-count}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale=.4]{../results/plane/pareto-plane-iso-best-balanced-legend.pdf}
    \caption{Predictability and parseability of 51 UD languages (red), indicated by ISO codes, compared to ten baseline word order grammars per language (green). Predictability and parseability scores are $z$-scored within language. Each point for a real language has a line pointing in the direction of the center of mass of its baselines. The green contour shows the density of baseline languages. Unlabeled dots represent the centroid for real languages (red), baseline languages (green), and languages optimized for predictability (yellow), parseability (pink), efficiency (blue), and dependency length (red). When a language is to the bottom--left of its baselines, this indicates that it is relatively optimal for efficiency.} % TODO colors, fontsize, etc could conceivably be made prettier
    \label{fig:pareto-plane}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.2]{../results/correlations/posterior-satisfied-universals-efficiency.pdf}
     \includegraphics[scale=.2]{../results/correlations/posterior-satisfied-universals-langmod.pdf}
     \includegraphics[scale=.2]{../results/correlations/posterior-satisfied-universals-parseability.pdf}
    \includegraphics[scale=.2]{../results/correlations/posterior-satisfied-universals-depl.pdf}
	\caption{Posterior of the number of correlations predicted in the direction found in the UD treebanks.}
    \label{fig:posterior-satisfied-count}
\end{figure}

### 2019-01-19 writeup/pnas-word-order-si.tex
rewired figure paths

    \includegraphics[scale=.25]{figures/coverage-langmod-best.pdf}
    \includegraphics[scale=.25]{figures/coverage-parse-best.pdf}
    \includegraphics[scale=.25]{figures/coverage-two-lambda09-best.pdf}

    \includegraphics[scale=.25]{figures/coverage-ground.pdf}
    \includegraphics[scale=.25]{figures/coverage-depl.pdf}
	\caption{Correlations satisfied by the best word order grammars for predictability, parseability, efficiency, by the UD languages, and by the best grammars for dependency length.}
    \label{fig:posterior-prevalence}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{figures/posterior_joint_with_ud.pdf}
	\caption{Posteriors of the prevalences of the correlations among languages optimized for Predictability (red), parseability (green), and efficiency (blue), controlling for languages and language families, with prevalence in the UD languages.}
    \label{fig:posterior-prevalence}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{figures/cky-parse.pdf} 
	\caption{Parsability loss $H[T|L_\theta(T)]$ (lower is better) computed by a simple CKY parser, for random word order grammars (red) and word order grammars optimized for efficiency (blue).}
    \label{fig:cky-parser}
\end{figure}

@@

    \includegraphics[scale=.5]{figures/adversarial-parse-loss-english.pdf}

@@

    \includegraphics[scale=.5]{figures/adversarial-parse-loss-japanese.pdf}
	\caption{Parseability of baseline grammars and grammars optimized for efficiency, in English (top) and Japanese (bottom), measured by parsing loss $H[T|L_\theta(T)]$ (lower is better), for the four distorted orderings, and the actual orderings (`real').}
    \label{fig:distorted-parser}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.4]{figures/bigrams.pdf} 
	\caption{Surprisal (lower is better) computed from Bigram model, on English and Japanese data ordered according to random ordering grammars (red) and ordering grammars optimized for efficiency (blue).}
    \label{fig:bigrams}
\end{figure}

>>>>

    \includegraphics[scale=.25]{../results/correlations/coverage-langmod-best.pdf}
    \includegraphics[scale=.25]{../results/correlations/coverage-parse-best.pdf}
    \includegraphics[scale=.25]{../results/correlations/coverage-two-lambda09-best.pdf}

    \includegraphics[scale=.25]{../results/correlations/coverage-ground.pdf}
    \includegraphics[scale=.25]{../results/correlations/coverage-depl.pdf}
	\caption{Correlations satisfied by the best word order grammars for predictability, parseability, efficiency, by the UD languages, and by the best grammars for dependency length.}
    \label{fig:posterior-prevalence}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{../results/correlations/posterior_joint_with_ud.pdf}
	\caption{Posteriors of the prevalences of the correlations among languages optimized for Predictability (red), parseability (green), and efficiency (blue), controlling for languages and language families, with prevalence in the UD languages.}
    \label{fig:posterior-prevalence}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{../results/cky/cky-parse.pdf} 
	\caption{Parsability loss $H[T|L_\theta(T)]$ (lower is better) computed by a simple CKY parser, for random word order grammars (red) and word order grammars optimized for efficiency (blue).}
    \label{fig:cky-parser}
\end{figure}

@@

    \includegraphics[scale=.5]{../results/permuted/adversarial-parse-loss-english.pdf}

@@

    \includegraphics[scale=.5]{../results/permuted/adversarial-parse-loss-japanese.pdf}
	\caption{Parseability of baseline grammars and grammars optimized for efficiency, in English (top) and Japanese (bottom), measured by parsing loss $H[T|L_\theta(T)]$ (lower is better), for the four distorted orderings, and the actual orderings (`real').}
    \label{fig:distorted-parser}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.4]{../results/bigrams/bigrams.pdf} 
	\caption{Surprisal (lower is better) computed from Bigram model, on English and Japanese data ordered according to random ordering grammars (red) and ordering grammars optimized for efficiency (blue).}
    \label{fig:bigrams}
\end{figure}
